---
title: "Vignette for Kyle Power's Tools"
author: "Kyle M. Power"
date: "March 4th, 2018"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## GGplot Examples
The same data `flightData` plotted 3 different ways.
```{r, fig.show='hold'}
library(PowerKyleTools)
library(ggplot2)
flightData <- read.csv("http://users.stat.umn.edu/~almquist/3811_examples/all_alaska_flights.csv")
ggplot2::ggplot(data = flightData, mapping = aes(x = dep_delay, y = arr_delay)) + 
  geom_boxplot()
ggplot2::ggplot(data = flightData, mapping = aes(x = dep_delay, y = arr_delay)) + 
  geom_point()
ggplot2::ggplot(data = flightData, mapping = aes(x = dep_delay, y = arr_delay)) + 
  geom_smooth()
```

## Examples
Calling `func1` on a data set will return a list containing the mean, variance, and standard deviation without running any data checks.
Calling `func2` on a data set will also return a list containing the mean, variance, and standard deviation, but first will check the data to make sure it is compatible.
```{r, fig.show='hold'}
library(PowerKyleTools)
d <- read.table(url("http://www.stat.umn.edu/geyer/3701/data/q1p4.txt"),header = TRUE)
func1(d)
```
Calling `func3` on a vector will compute the Maximum Liklihood Estimation for a gamma distribution and return the scalar result.
```{r, fig.show='hold'}
library(PowerKyleTools)
v <- (1:10)
func3(v)
```
Calling `func4` on a data.frame will compute the weighted mean, variance, and standard deviation and return it as a list.
```{r, fig.show='hold'}
library(PowerKyleTools)
d <- read.table(url("http://www.stat.umn.edu/geyer/3701/data/q1p4.txt"),header = TRUE) 
func4(d)
```
Calling `func5` on a data.frame will compute the weighted mean, variance, and standard deviation and return it as a list, but will first check to make sure data frame contains compatible data.
```{r, fig.show='hold'}
library(PowerKyleTools)
d <- read.table(url("http://www.stat.umn.edu/geyer/3701/data/q1p4.txt"),header = TRUE) 
func5(d)
```
Calling `func6` on a data set will run a check to make sure that data is compatible, and will throw an error if data is not numeric, finit, zero lenth, NA, NAN.
```{r, fig.show='hold'}
library(PowerKyleTools)
d <- read.table(url("http://www.stat.umn.edu/geyer/3701/data/q1p4.txt"),header = TRUE) 
func6(d)
```
Use `func7` to compute the liklihood of a given distribution for data x, and return the scalar result.
```{r, fig.show='hold'}
library(PowerKyleTools)
x1 = rgamma(100,3)
func1 = function(theta, x) dgamma(x, shape = theta, log = TRUE)
result7_gamma <- func7(x1,func1,c(0,3))
```

Use `matMult` to compute the scalar result of $$x^T A^{-1} x$$
```{r, fig.show='hold'}
library(PowerKyleTools)
load(url("http://www.stat.umn.edu/geyer/3701/data/q2p1.rda"))
matMult(a, x)
```
Use `stdize` to compute the standardized result of a 2-D matrix by column.
```{r}
library(PowerKyleTools)
load(url("http://www.stat.umn.edu/geyer/3701/data/q2p1.rda"))
stdize(a)
```